---
title: "Emily in Terasse"
output: html_document
date: "2026-1-13"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r library, include=FALSE}
library(tidyverse) #for data cleaning
library(ggplot2)  #for plot
```

```{r Dataset, include=FALSE}
ds <- read_csv2(file = "terrasses-autorisations.csv" )
```

# Emily in terasse

## Brief introduction to the French tradition of terrasse 

<p> "Aller en terrasse" is the tradition for the French. The fact of going to drink and eat some snacks in an outdoor place. 
It could look casual but it is a fundamental social institution and a cornerstone of the French art de vivre.
It brings people from different horizons all in the same place. It's a real social place for French people who 
like to spend time there. It's very unique and very different from other European cultures. 
These terraces are often closed in winter and reopen in summer. This makes us able to 
count the number of terraces open every year and so, to perform this cultural data analysis </p>


# The terasse from Paris 

```{r Dataset cleaning and map, include=FALSE}
ds_map <- ds %>% separate(geo_point_2d, into = c("lat", "lng"), sep = ", ") %>%
  mutate(
    lat = as.numeric(lat),
    lng = as.numeric(lng)
  )
```


